Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-10 _02_filtering_data.Rmd
update code and fig name in rmd
edit figure 2

# to plot
library(ggplot2)
library(patchwork)
```

@@

```{r echo=FALSE}
# plot data inside and outside bbox
fig_filter_bounds <-
  ggplot() +
  geom_point(
    data = data_inside_bbox,
    aes(x, y),
    col = pal[3],
    alpha = 1, size = 0.2
  ) +
  geom_point(
    data = data_copy[!data_inside_bbox,
      on = c("x", "y")
    ],
    aes(x, y),
    col = "grey",
    shape = 4,
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  geom_hline(
    yintercept = c(0.5, 1),
    col = "grey",
    lty = 2
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  theme(plot.background = element_rect(fill = NA)) +
  coord_equal(expand = T)
```

@@

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot() +
  geom_path(
    data = data_copy,
    aes(x, y),
    col = "grey",
    lwd = 0.2
  ) +
  geom_point(
    data = data_copy[500:800, ],
    aes(x, y),
    # size = 0.5,
    alpha = 0.6,
    shape = 4, col = "grey30"
  ) +
  geom_point(
    data = data_copy[!data_copy[500:800, ],
      on = c("x", "y")
    ],
    aes(x, y,
      col = (in_speed >= 0.03 & out_speed >= 0.03),
      shape = (in_speed >= 0.03 & out_speed >= 0.03),
      size = (in_speed >= 0.03 & out_speed >= 0.03)
    ),
    show.legend = F,
    alpha = 1
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  scale_color_manual(values = c(pal[3], "grey")) +
  scale_shape_manual(values = c(1, 4)) +
  scale_size_manual(
    values = c(0.2, 2)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_equal() +
  theme(plot.background = element_rect(fill = NA))
```

@@

![](figures/fig_03_filter_speed.png)

>>>>

# to plot
library(ggplot2)
library(patchwork)
library(ggthemes)
```

@@

```{r echo=FALSE}
# plot data inside and outside bbox
fig_filter_bounds <-
  ggplot() +
  geom_path(
    data = data_copy,
    aes(x, y),
    col = "grey",
    lwd = 0.2
  ) +
  geom_point(
    data = data_inside_bbox,
    aes(x, y),
    col = pal[3],
    alpha = 1, size = 0.2
  ) +
  geom_point(
    data = data_copy[!data_inside_bbox,
      on = c("x", "y")
    ],
    aes(x, y),
    col = "grey",
    shape = 4,
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  geom_hline(
    yintercept = c(0.5, 1),
    col = "grey",
    lty = 2
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  theme(plot.background = element_rect(fill = NA)) +
  coord_equal(expand = T)
```

@@

Histogram of speed

```{r}
fig_hist_speed =
  ggplot()+
  geom_histogram(
    data = data_copy,
    aes(x = in_speed,
        fill = ifelse(in_speed > 0.05, "outlier", "good")),
    position = position_identity(),
    bins = 60
  )+
  geom_histogram(
    data = data_copy[500:800, ],
    aes(x = in_speed),
    fill = pal[4],
    bins = 60
  )+
  geom_vline(
    xintercept = 0.05,
    # size = 0.2,
    lty = 2
  )+
  annotate(
    geom = "text",
    x = 0.11,
    y = 150,
    label = "Threshold",
    size = 4,
    angle = 90
  )+
  scale_fill_manual(
    values = c(
      "outlier" = pal[1],
      "good" = "grey"
    )
  )+
  scale_y_sqrt()+
  scale_x_log10(
  )+
  theme_test(base_family = "sans")+
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(
      face = "bold"
    ),
    plot.background = element_blank()
  )+
  labs(
    title = "(c)",
    x = "Speed"
  )
```

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot() +
  geom_path(
    data = data_copy,
    aes(x, y,
        col = ifelse(in_speed >= 0.05 | out_speed >= 0.05, 
                     "outlier_path", "good_path"),
        group = NA),
    lwd = 0.2
  ) +
  geom_point(
    data = data_copy[500:800, ],
    aes(x, y),
    # size = 0.5,
    alpha = 0.6,
    # stroke = 1,
    shape = 4, col = pal[4]
  ) +
  geom_point(
    data = data_copy[!data_copy[500:800, ],
      on = c("x", "y")
    ],
    aes(x, y,
      col = ifelse(in_speed >= 0.03 & out_speed >= 0.03, "outlier", "good"),
      shape = (in_speed >= 0.03 & out_speed >= 0.03),
      size = (in_speed >= 0.03 & out_speed >= 0.03)
    ),
    show.legend = F,
    alpha = 1
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  annotation_custom(
    grob = ggplotGrob(
      fig_hist_speed
    ),
    xmin = 0.80,
    xmax = 1.08,
    ymin = 0.25,
    ymax = 0.6
  )+
  scale_color_manual(values = c(
    "outlier_path" = "red",
    "good_path" = "grey",
    "good" = pal[3], 
    "outlier" = "red")) +
  scale_shape_manual(values = c(1, 4)) +
  scale_size_manual(
    values = c(0.2, 2)
  ) +
  ggthemes::theme_few(
    base_family = "Arial"
  ) +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    legend.position = "none"
  ) +
  coord_equal() +
  theme(plot.background = element_rect(fill = NA))
```

@@

![](figures/fig_02_filtering_data.png)
